
\begin{achievement}%成果
    \begin{enumerate}[1.]
        \item 已发表的论文
            \begin{enumerate}[(1)]
                \item Xirong Li, \textbf{Chaoxi Xu}, Xiaoxu Wang, Weiyu Lan, Zhengxiong Jia, Gang Yang, Jieping Xu: COCO-CN for Cross-Lingual Image Tagging, Captioning and Retrieval. IEEE Transactions on Multimedia (T-MM), 2019. (SCI，CCF B类期刊，影响因子5.452)
                \item Jianfeng Dong, Xirong Li, \textbf{Chaoxi Xu}, Shouling Ji, Yuan He, Gang Yang, Xun Wang: Dual Encoding for Zero-Example Video Retrieval. IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2019. (CCF A类会议，计算机视觉顶级会议）
                \item \textbf{Chaoxi Xu}, Xiangjia Zhu, Wenwen He, Yi Lu, Xixi He, Zongjiang Shang, Jun Wu, Keke Zhang, Yinglei Zhang, Xianfang Rong, Zhennan Zhao, Lei Cai, Dayong Ding, Xirong Li: Fully Deep Learning for Slit-lamp Photo based Nuclear Cataract Grading. International Conference on Medical Image Computing and Computer Assisted Intervention (MICCAI), 2019. (医学影像分析高水平会议)
                \item Xirong Li, \textbf{Chaoxi Xu}, Gang Yang, Zhineng Chen, Jianfeng Dong: W2VV++: Fully Deep Learning for Ad-hoc Video Search. ACM international conference on Multimedia (ACM MM), 2019. (CCF A类会议)
                \item Jianfeng Dong, Xun Wang, Leimin Zhang, \textbf{Chaoxi Xu}, Gang Yang, Xirong Li: Feature Re-Learning with Data Augmentation for Video Relevance Prediction. IEEE Transactions on Knowledge and Data Engineering (TKDE), 2019. (CCF A类期刊，影响因子3.857)
            \end{enumerate}

        \item 参加与研究方向相关的国际评测
            \begin{enumerate}[(1)]
                \item 2018年 美国国家标准与技术研究院TRECVID 2018即席视频检索任务（Ad-hoc Video Search）第一名
                \item 2018年 Hulu与ACM Multimedia 2018联合举办的基于内容的视频相关性预测比赛分别在Movies和TV shows两个子任务上取得了第一名和第二名
                \item 2017年 美国国家标准与技术研究院TRECVID 2017视频与文本匹配和排序任务（matching and ranking task）第二名
            \end{enumerate}
    \end{enumerate}

\end{achievement}
